Comparing Apples and Oranges in Youth Depression Treatments?

### 2024-09-23 multilevel_metaregression/manuscript_with_multilevel_metan.qmd
fixed figures

 png("plot_means_multi_all.png", width=6.5, height=4, units="in", res=300)
 plot_means_multi_all
 dev.off()

@@

 png("plot_means_multi_no_wl.png", width=6.5, height=4, units="in", res=300)
plot_means_no_wl
 dev.off()

@@

png("plot_means_multi_clin.png", width=6.5, height=4, units="in", res=300)
plot_means_clin
dev.off()

@@

 png("plot_means_multi_cdrs.png", width=6.5, height=4, units="in", res=300)
 plot_means_cdrs
 dev.off()

@@

 png("plot_means_multi_hamd.png", width=6.5, height=4, units="in", res=300)
 plot_means_multi_hamd
 dev.off()

@@

 png("plot_means_multi_sd.png", width=6.5, height=4, units="in", res=300)
 plot_means_multi_sd
 dev.off()
```

@@

 png("plot_means_multi_var2.png", width=6.5, height=4, units="in", res=300)
 plot_means_multi_var2
 dev.off()
```

>>>>

 png("plot_means_multi_all.png", width=6.5, height=6, units="in", res=300)
 plot_means_multi_all
 dev.off()

@@

 png("plot_means_multi_no_wl.png", width=6.5, height=6, units="in", res=300)
plot_means_no_wl
 dev.off()

@@

png("plot_means_multi_clin.png", width=6.5, height=6, units="in", res=300)
plot_means_clin
dev.off()

@@

 png("plot_means_multi_cdrs.png", width=6.5, height=6, units="in", res=300)
 plot_means_cdrs
 dev.off()

@@

 png("plot_means_multi_hamd.png", width=6.5, height=6, units="in", res=300)
 plot_means_multi_hamd
 dev.off()

@@

 png("plot_means_multi_sd.png", width=6.5, height=6, units="in", res=300)
 plot_means_multi_sd
 dev.off()
```

@@

 png("plot_means_multi_var2.png", width=6.5, height=6, units="in", res=300)
 plot_means_multi_var2
 dev.off()
```
